---
title       : "Developing Data Products"
subtitle    : "A presentation for the Coursera DS Certification class"
author      : "Austin T"
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---

## Project Purpose

The purpose of my Shiny App is to illustrate the process by which a Linear Regression line is calculated.

- The app can be found here at [ShinyApps.io](https://atidmore.shinyapps.io/9DDP)  
- The source code can be found on [GitHub](https://github.com/ATidmore/DataProducts_Project/tree/master)

--- .class #id 

## The Data
Using the built-in "mtcars" dataset in R, I modeled a simple relationship between the car's weight ("wt") and its fuel efficiency ("mpg"). We can see that the data points are negatively correlated.

```{r echo = FALSE, message=FALSE}
data(mtcars)
require(ggplot2)
```

```{r echo=FALSE}
g <- ggplot(data = mtcars, aes(x = wt, y = mpg))
g <- g + geom_point(color = "#00CC66")
g
```


---

## The Application

The application will allow a user to learn how a Linear Regression line is created by optimizing the position of the line his/herself. A message displays to the user if he/she optimized the line - according to the Least Squares method (excerpt below).
```{r echo = FALSE}
g <- g + geom_abline(int = 37.3, slope = -5.3, color = "steelblue", size = 1)
g
```

---
## Conclusion

I hope you enjoyed using my ShinyApp to find the optimal Linear Regression line! 

Best of luck to you as you continue on the Coursera Data Science Certification. 